Practical Considerations for Lomb-Scargle Periodic Analysis

### 2016-11-15 paper.tex
some tweaks to the paper

\subsubsection{Fourier Transform and Periodic Functions}

@@

Using the above definitions, it is straightforward to show that a time-offset in a function leads to a multiplicative phase in the Fourier transform; that is, if
\begin{equation}
  g_\tau(t) \equiv g(t - \tau)
\end{equation}
then 
\begin{equation}
  \mathcal{F}\{g_\tau\} = e^{-2\pi i \nu \tau}\mathcal{F}\{g\}
\end{equation}
Because the phase merely represents the chosen coordinate system, we'd like to remove it for spectral analysis.
One way to do this is to compute the power spectral density, which is proportional to \todo{const of proportionality?} the squared modulus of the Fourier Transform:
\begin{equation}
  P\{g\} \propto \left| \mathcal{F}\{g\} \right|^2.
\end{equation}
Because the modulus of a phase is equal to unity, the resulting measure is unchanged under time-translations in $g(t)$.

@@

@@

>>>>

\subsubsection{$\mathcal{F}$ of a Gaussian is a Gaussian}
One of the special functions under a Fourier transform is the Gaussian distribution, which is proportional to

\subsubsection{$\mathcal{F}$ of a Periodic Function is a Delta Function}

@@

Using the above definitions, it is straightforward to show that a time-offset in a function leads to a multiplicative phase in the Fourier transform; that is, if
\begin{equation}
  g_\tau(t) \equiv g(t - \tau)
\end{equation}
then 
\begin{equation}
  \mathcal{F}\{g_\tau\} = e^{-2\pi i \nu \tau}\mathcal{F}\{g\}
\end{equation}
Because the phase merely represents the chosen coordinate system, we'd like to remove it for spectral analysis.
One way to do this is to compute the power spectral density, which is proportional to \todo{const of proportionality?} the squared modulus of the Fourier Transform:
\begin{equation}
  P\{g\} \propto \left| \mathcal{F}\{g\} \right|^2.
\end{equation}
Because the modulus of a phase is equal to unity, the resulting measure is unchanged under time-translations in $g(t)$, and $P\{g\} = P\{g_\tau\}$ for any time-shift $\tau$.

@@

\section{From Idealistic to Realistic}

All of the above theory is beautiful and elegant, but when the theory meets the real world things get a bit more messy.
In particular, we rarely (if ever) are able to measure continuous functions like $g(t)$, but instead measure discrete realizations of the underlying function at a finite number of particular times $t_n$.
These discrete observations are effectively a window function over our data, and as we saw above, the presence of such a window function will propagate through our computation of the Fourier power!
The quantitative result of this windowning depends on the exact nature of the observation pattern; we will first consider the somewhat simpler case of evenly-spaced discrete data.

@@

Let's first consider the case of a large series of evenly-spaced observations.
Discrete samples can
